A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-11 MSRChallenge2016.tex
update java project count

First, we broadly characterize bug-fixing commits to Java code.  In this paper,
we study the \emph{September 2015/Github} dataset on Boa, including $7,830,023$
Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
fixing.

@@

Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
cover 14.78\% of buggy files. In the dataset studied by Kim et al., the overall
10 patterns cover almost 30\% of real patches~\cite{kim2013}. Although we only analyze 8
out of 10 bug fixing patterns, it is unlikely the final two will cover the
difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we are still assuming that the patterns never appear together. 
%Moreover, our detection is imprecise, and might represent an upper bound. 
This suggests that these fixing patterns might not generalize
beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.

>>>>

First, we broadly characterize bug-fixing commits to Java code.  In this paper,
we study the \emph{September 2015/Github} dataset on Boa, including $554,864$
Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
fixing.

@@

Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
cover 14.78\% of buggy files. In the dataset studied by Kim et al., the overall
10 patterns cover almost 30\% of real patches~\cite{kim2013}. Although we only analyze 8
out of 10 bug fixing patterns, it is unlikely the final two will cover the
difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we still assume that the patterns never appear together. 
%Moreover, our detection is imprecise, and might represent an upper bound. 
This suggests that these fixing patterns might not generalize
beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.
